### 2015-02-06 paper_30_measure.tex
added a sentence
adding info about 3 focus areas and 3 questions
fix some more minor typos

Anything can be measured \cite{Hubbard2010}.

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
    \end{itemize}

@@

A common technique for organization to measure themselves is a balanced scorecard.
A \textit{balanced scorecard} must contain the following six
characteristics.
\begin{enumerate}
  \item Financial 
  \item Customer Focus
  \item Environment/Community
  \item Internal Process
  \item Employee Satisfaction
  \item Learning and Growth
\end{enumerate}

Balanced scorecards are great for displaying the important information about
and organization.  However, a balanced scorecard does not specify what
exactly needs to be tracked.  It is also not specific to an SDO and 
it does not produce a single number.

@@

\subsection{COMBINING THE MEASURES TO FORM MPI}

>>>>

Anything can be measured \cite{Hubbard2010}.  An SDO
how numerous metrics.

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD\footnote{PMD is a source code analysis product.  It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
    \end{itemize}

@@

A common technique for organizations to measure themselves is a balanced scorecard.
A \textit{balanced scorecard} must contain the following six
characteristics.
\begin{enumerate}
  \item Financial 
  \item Customer Focus
  \item Environment/Community
  \item Internal Process
  \item Employee Satisfaction
  \item Learning and Growth
\end{enumerate}

Balanced scorecards are great for displaying the important information about
an organization.  However, a balanced scorecard does not specify what
exactly needs to be tracked.  It is also not specific to an SDO and 
it does not produce a single number.

@@

\subsection{COMBINING THE MEASURES}

### 2015-02-06 paper_50_sdlc-ae.tex
fix some more minor typos

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   layout the structure of tables and relationships necessary to the store all the data
   within a relational database such as MySQL or PostgreSQL.  Eventually,
   database diagrams and SQL scripts will be provided in the section.

>>>>

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   lay out the structure of tables and relationships necessary to the store all the data
   within a relational database such as MySQL or PostgreSQL.  Eventually,
   database diagrams and SQL scripts will be provided in the section.
